\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-20 forwards-and-backwards.tex
.

%%%%%%% notation
\newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
\newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
\newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
\newcommand{\kernel}{\rho}  % interaction kernels
\newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
\newcommand{\wavespeed}{\mathfrak{c}}    % speed (vector) of a wave
\newcommand{\Lgen}{\mathcal{L}}    % generator of a lineage
\newcommand{\Pgen}{\mathcal{P}}    % generator of the population process
\newcommand{\lp}{\xi}              % process with levels

@@

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{Evolution of an Individual Particle}
\label{sec: Evolution of an Individual Particle}

>>>>

%%%%%%% notation
\newcommand{\DG}{\mathcal{B}}  % generator of the dispersal process
\newcommand{\meanq}{\vec b}    % mean of dispersal, times theta
\newcommand{\covq}{\Sigma}     % covariance matrix of dispersal, times theta
\newcommand{\kernel}{\rho}  % interaction kernels
\newcommand{\smooth}[1]{\kernel_{#1} \! * \!}  % convolution by the interaction kernel
\newcommand{\wavespeed}{\mathfrak{c}}    % speed (vector) of a wave
\newcommand{\Lgen}{\mathcal{L}}    % generator of a lineage
\newcommand{\Pgen}{\mathcal{P}}    % generator of the population process
\newcommand{\lp}{\xi}              % process with levels
\newcommand{\labelspace}{\mathcal{I}} % space of labels

@@

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{Construction of individual lineages}

Although we will \comment{later} show convergece of the lookdown process
defined by Definition~\ref{defn:lookdown_mgale}
to a stochastic process in which individuals retain their identities,
it is convenient to construct the lookdown process
in a way that explicitly represents the motion of each individual and their offspring.
This will then make obvious how linages move in the limit.

To construct the process, each individual will have a label in $\labelspace = \bigcup_{k > 1} \IN^k$,
in such a way that offspring's labels are formed by appending a unique integer
onto their parent's label (i.e., a Ulam-Harris scheme).
The behavior of each individual is driven by an associated Poisson process:
for each label $\ell \in \labelspace$
we associate a Poisson random measure $\Pi_\ell$
on $[0, \infty)^2 \times \IR^d \times \{0, 1\}$.
The mean measure is a product measure:
on $[0, \infty)^2$ it is Lesbegue,
on $\IR^d$ it is the dispersal distribution (i.e., $q(0, \cdot)$),
and on $\{0, 1\}$ it is $\frac{1}{2} \delta_0 + \frac{1}{2} \delta_1$
(i.e., a coin flip).
If a point in $\Pi_\ell$ is $(s, v, y, \kappa)$, that will mean that
$s$ is a potential birth time for individual $\ell$,
$v$ is used to determine the new level,
$y$ is the new location relative to that of $\ell$'s location,
and $\kappa$ is used to determine whether the parent or child takes the new level.

To begin,
each individuals alive at time zero is indexed by a positive integer.
Then

%% %% %% %% %% %% %% %% %% %% %% %%
\subsection{PREVIOUS VERSION OF Evolution of an Individual Particle}
\label{sec: Evolution of an Individual Particle}
